Automating Verification of MPC Security

### 2023-06-09 popl24/hyperprop.tex
checkpoint

As for noninterference, we can show that $\NIMO$ is equivalent
to saying that a given program does not change the probability
of honest secrets conditioned on corrupt secrets and views
(including the output view), as compared to conditioning on
just the corrupt secrets and input. In addition to providing
insights about $\NIMO$, this form is helpful for
verification techniques. 
\begin{lemma}
  Given $H$, $C$, and a program $\prog$ with $\iov(\prog) = (S,V)$ and
  output view $x \in V$
  $\prog$ satisfies noninterference modulo output iff for all
  $\store \in \mems(S \cup V)$:
  $$\margd{(\condd{\progd(\prog)}{\store_{(S \cup \{x\})_C}})}{S_H} =
    \margd{(\condd{\progd(\prog)}{\store_{(S\cup V)_C}})}{S_H} $$
\end{lemma}

>>>>

As for noninterference, we can show that $\NIMO$ is equivalent
to saying that a given program does not change the probability
of honest secrets conditioned on corrupt secrets and views
(including the output view), as compared to conditioning on
just the corrupt secrets and input. In addition to providing
insights about $\NIMO$, this form is helpful for
verification techniques. 
\begin{lemma}
  $\NIMO(\prog)$ iff for all $H$ and $C$ with $|C| \le |H|$ and
  $\store \in \mems(S \cup V)$:
  $$\margd{(\condd{\progd(\prog)}{\store_{(S \cup \{\outv\})_C}})}{S_H} =
  \margd{(\condd{\progd(\prog)}{\store_{(S\cup V)_C}})}{S_H} $$
  where  $\iov(\prog) = (S,V)$.
\end{lemma}
